### 2023-05-22 docs/minutes/slides_25_05/document.tex
broaden sigma_p prior

\date{EE/GW meeting, May 19, 2023}

@@

		Last time: Problems at small $h$, nasty likelihood curves

	All likelihood curves for $\bar{\theta}_{\rm GW}$:

\includegraphics[width=0.9\textwidth,height=0.7\textwidth]{images/all_likelihood_curves}

@@

>>>>

\date{EE/GW meeting, May 25, 2023}

@@

		Last time:

\includegraphics[width=0.85\textwidth,height=0.85\textwidth]{images/canonical12_result}

@@

	Last time:

	\begin{itemize}
		\item Earth terms model $g'(\tau; \bar{\theta}) = 1 - \frac{1}{2} \frac{ H_{ij}q^i q^j }{(1 + \bar{n}\cdot \bar{q}) } \left[ \cos(-\Omega \tau +\Phi_0) \right]$
		\item Zero process noise  $\sigma_p = 0$
		\item No heterodyning
		\item Single noise realisation
    \end{itemize}

	This time:

	\begin{itemize}
		\item Earth terms model 
		\item \alert{Non - Zero process noise  $\sigma_p \neq 0$}
		\item \alert{Heterodyning}
		\item \alert{Multiple noise realisations}
	\end{itemize}

	Reminder of "heterodyned" equations

	Note the distinction between $ f_{\rm EM}$ and $f^{\, *}_{\rm EM}$

	$f_{\rm EM}$ is the exact, true solution parametrised by the unknowns $f_0, \dot{f}_0$. This heterodyning is just a change of variables

	$f^{\, *}_{\rm EM}$ is a guess of $f_{\rm EM}$ based on the pulsar ephemeris. It is just to scale the equations - it does not remove any degrees of freedom - we still are estimating $f_0, \dot{f}_0$ optimally!

	\begin{equation}
		\frac{df \, '}{dt} = - \gamma f \, '  + \xi 
	\end{equation}

	\begin{eqnarray}
		f \, '_{\rm M} = (1 - X)f \, ' - X f_{\rm EM} + \alert{(f_{\rm EM} - f^{\, *}_{\rm EM})} +  N_{\rm G}
	\end{eqnarray}
